\Sof{TBA - New Titles in the comments}

### 2020-05-15 paper/icsme20.tex
motivation on hold

As an example, consider the patch of the TLS state machine protocol implementation
in OpenSSL\footnoteref{openssl} to address a memory leak flaw found in the way 
OpenSSL handled TLS status request extension data during session 
renegotiation and where a malicious client could cause a Denial-of-Service
(DoS) attack via large OCSP Status Request extensions - if OCSP stapling support
enabled. Online Certificate Status Procotol (OCSP) stapling, formally known as the TLS Certificate 
Status Request extension, is a standard for checking the revocation status of
certificates.

@@

>>>>

\Sof{Waiting for final results --}As an example, consider the patch of the TLS state machine protocol implementation
in OpenSSL\footnoteref{openssl} to address a memory leak flaw found in the way 
OpenSSL handled TLS status request extension data during session 
renegotiation and where a malicious client could cause a Denial-of-Service
(DoS) attack via large OCSP Status Request extensions - if OCSP stapling support
enabled. Online Certificate Status Procotol (OCSP) stapling, formally known as the TLS Certificate 
Status Request extension, is a standard for checking the revocation status of
certificates.

@@

\Sof{-- Waiting for final results}
